Analysis paper

### 2021-05-22 analysis/analysis.Rmd
add tables for different phases

```{r}
# create helper function to make table
make_score_table <- function(scores) {
  scores <- as.data.table(scores)
  setnames(scores, 
           old = c("model", "target_type", "interval_score", "aem", 
                   "relative_skill", "scaled_rel_skill", "sharpness", 
                   "underprediction", "overprediction", "bias", 
                   "50", "90"), 
           new = c("Model", "Target", "WIS", "Abs. error", 
                   "rel. skill", "Skill", "Sharpness", 
                   "Underpred.", "Overpred.", "Bias", 
                   "50%-Cov.", "90%-Cov."))

@@

```{r fig.height=10, fig.width=15}
scores %>%
  gridExtra::tableGrob(theme = theme_minimal(), rows = NULL)
```

@@

(p_combined + p) / p_phases + 
  plot_layout(guides = "collect") & 
  plot_annotation(tag_levels = 'A') &
  theme(legend.position = 'bottom')

ggsave("plots/distribution_scores.png")

>>>>

```{r}
# create helper function to make table
make_score_table <- function(scores) {
  scores <- as.data.table(scores)
  setnames(scores, 
           old = c("model", "target_type", "interval_score", "aem", 
                   "relative_skill", "scaled_rel_skill", "sharpness", 
                   "underprediction", "overprediction", "bias", 
                   "50", "90", "location_target", "target_phase"), 
           new = c("Model", "Target", "WIS", "Abs. error", 
                   "rel. skill", "Skill", "Sharpness", 
                   "Underpred.", "Overpred.", "Bias", 
                   "50%-Cov.", "90%-Cov.", "Target", "Target"), 
           skip_absent = TRUE)

@@

@@

coverage_tables <- eval_forecasts(
  filtered_data[grepl("2", target)], 
  summarise_by = c("model", "target_phase", "classification", "range"), 
  compute_relative_skill = TRUE, 
  baseline = "Baseline"
)[range %in% c(50, 90), 
                   .(model, target_phase, coverage, classification, range)] %>%
  dcast(formula = ... ~ range, value.var = "coverage")

scores_tables <- eval_forecasts(
  filtered_data[grepl("2", target)], 
  summarise_by = c("model", "target_phase", "classification"), 
  compute_relative_skill = TRUE, 
  baseline = "Baseline"
)

tbl <- scores_tables %>%
  merge(coverage_tables, all.x = TRUE, by = c("modellocation_target", "target_phase", "classification"))

tables <- list()
table_dfs <- list()
targets <- unique(tbl$target_phase)

for (tar in targets) {
  tables[[tar]] <- make_score_table(tbl[target_phase == tar])
}

for (tar in targets) {
  table_dfs[[tar]] <- tbl[target_phase == tar, 
                          .("Model" = model, 
                            # "Target" = target_phase,
                            "WIS" = interval_score,
                            # "Rel. skill" = scaled_rel_skill, 
                            "Sharpn." = sharpness, 
                            "Underp.." = underprediction, 
                            "Overp." = overprediction)#, 
                            # "Bias" = bias,
                            # "50%-Cov." = `50`, 
                            # "90%-Cov." = `90`)
                          ]
  table_dfs[[tar]] <- table_dfs[[tar]][, lapply(.SD, FUN = function(x) {
    if (is.numeric(x)) {
      return(round(signif(x, 3), 2))
    } else {
      return(x)
    }
  })]
}

pl <- (p_combined + p) / p_phases + 
  plot_layout(guides = "collect") & 
  plot_annotation(tag_levels = 'A') &
  theme(legend.position = 'bottom')

print(pl)
ggsave("plots/distribution_scores.png")

# make plots with tables
library(gridExtra)

tbl_plt <- grid.arrange(tableGrob(table_dfs[[1]]), 
             tableGrob(table_dfs[[2]]), 
             tableGrob(table_dfs[[3]]), 
             tableGrob(table_dfs[[4]]), 
             tableGrob(table_dfs[[5]]), 
             tableGrob(table_dfs[[6]]), 
             nrow = 2)

print(tbl_plt)
ggsave("plots/distribution_scores_table.png")
